---
title: "101afp"
output: html_document
date: "2025-06-02"
---


```{r}
data <- read.csv("Data - FINAL DATA.csv")
data
library(tidyverse)
library(car)
```

# POWER ANALYSIS

```{r}
library(pwr)
fval <- 1.074/ sqrt(4.80)
fval
pwr.anova.test(k = 9, f = 0.4902117, sig.level = 0.05, power = 0.95)
```


R output indicated a required sample size of 11.41 per treatment group, which we rounded up to 12. Therefore, the total number of participants needed for the experiment is 12×9=108 student


# ANOVA

```{r}
data <- data %>%
  mutate(
    caffeine = factor(caffeine, levels = c("Coffee", "Tea", "Energy Drink")),
    exercise = factor(exercise, levels = c("Light Jogging", "Relaxing Walk Outdoors", "Stretching and Holding")),
    block = factor(block)
  )


model <- aov(diff ~ caffeine * exercise + block, data = data)
summary(model)

```

# ADEQUACY PLOTS 

```{r}
plot(model)
```

All assumptions appear to be satisfied with no major deviations


# INTERACTION PLOT



```{r}
library(ggplot2)
library(dplyr)


means <- data %>%
  group_by(caffeine, exercise) %>%
  summarise(mean_diff = mean(diff), .groups = "drop")


ggplot(means, aes(x = caffeine, y = mean_diff, group = exercise, color = exercise)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  labs(
    title = "Interaction Plot: Exercise × Caffeine",
    x = "Caffeine Type",
    y = "Mean Memory Score Difference",
    color = "Exercise Type"
  ) +
  theme_minimal()

```


There is no interaction between caffeine type and exercise - lines are roughly parallel (p=0.634) for interaction

# POST HOC

```{r}

tukey_results <- TukeyHSD(aov(diff ~ caffeine * exercise + block, data = data), "caffeine")

as.data.frame(tukey_results$caffeine)

```


Energy Drink resulted in significantly greater memory improvement compared to both Coffee (p = 0.031) and Tea (p = 0.006). No other pairwise comparisons among caffeine types were statistically significant (p > 0.05)
